\chapter{INTRODUCTION}
\section{Motivation}
In recent years, international interest in cislunar missions and operations has rapidly increased.
This is evidenced by the development of infrastructure for the National Aeronautics and Space
Administration's (NASA) Gateway program, a long-term hub that will reside in an Earth-Moon
Near-Rectilinear Halo Orbit (NRHO) in the lunar vicinity\cite{Zamora:2024}. While there are a lot
of exciting opportunities for cislunar missions, periodic orbits and dynamical structures in this
region of space can also be exploited as stepping stones on the way to deep-space exploration. In
its 2022 Strategic Plan, NASA outlines goals to "Extend human presence to the Moon and on towards
Mars for sustainable long-term exploration, development, and utilization" and "Enhance space access
and services"\cite{NASA:2022s}, that are further supported by its "Moon to Mars Objectives"
document released that same year\cite{NASA:2022m}. These documents support the idea that operations
and infrastructure in the cislunar region can be employed to support future missions to Mars and
other deep-space targets.

Unlike Earth orbits, periodic orbits and trajectories in cislunar space exist in a complex
multi-body dynamical regime that is significantly affected by gravitational forces from both the
Earth and the Moon (and in some cases the Sun). While the addition of these forces introduces new
challenges to the trajectory design process, it also provides opportunities to leverage elements of
dynamical systems theory in ways that are not possible with standard Keplerian dynamics. These
elements include unstable families of periodic orbits with stable and unstable invariant manifolds
that are useful for constructing transfers between orbits. These techniques are currently employed
to design missions in the cislunar region and similar strategies can be adapted and applied to
construct transfers between cislunar orbits and deep-space targets residing outside of the Earth
region.

NASA's goal of establishing a permanent presence on Mars necessitates more efficient and adaptable
transfer strategies for missions since traditional approaches have high maneuver costs and are
inflexible. In the past, NASA and other space agencies have designed and executed uncrewed
interplanetary missions to Mars. However, their goal to develop a human presence on Mars in the
near future requires an increase in both crewed and uncrewed missions to the Martian vicinity,
highlighting the need for low-cost, reliable transfer strategies. Traditionally, uncrewed
interplanetary missions depart directly from the Earth with high-energy transfers\cite{Drake:2009}.
Not only do these solutions have a high propellant cost, but they are also point solutions that
need to be recomputed whenever a mission parameter changes. As humankind prepares for sustained
exploration of Mars, the development of more cost-effective and flexible mission strategies is
crucial to ensure success.

An alternative option is to depart from a cislunar orbit, perhaps after refueling at a servicing
depot, decreasing the propellant costs for both the launch from the surface of Earth and the
interplanetary transfer. The past successful applications of multi-body dynamical systems theory to
cislunar transfer design suggest that these techniques can also be applied to deep-space transfers
with similar performance. Utilizing unstable periodic orbit families and invariant manifold theory
allows for lower-energy and lower-cost departures from the Earth-Moon system. After departure,
patched dynamical models and existing transfer techniques are employed to complete the construction
of end-to-end transfers from the Earth-Moon system to deep-space destinations. One consequence of
this approach is that invariant manifolds often increase the trajectory time-of-flight. While long
times-of-flight are not desirable characteristics for manned missions due to radiation and other
concerns, it is an acceptable trade-off for cargo and supply missions. Consequently, rather than
focusing on optimizing the interplanetary transfer itself, comparing available unstable periodic
orbit families leads to insight into time-efficient departures from the Earth-Moon system. The
exploitation of simplified dynamical models also provides families of transfers instead of point
solutions, adding flexibility to the mission design process. Incorporating these dynamical
techniques into mission planning offers a more flexible approach to deep-space transfers.

\section{Research Objectives}
To sustain an increase in missions to Mars and other deep-space targets, a framework for lower-cost
transfers from the Earth region is necessary. One promising avenue to decrease propellant costs is
to utilize invariant manifold theory for low-energy departures from unstable multi-body periodic
orbits in the cislunar region. Since the application of multi-body dynamical systems theory to
cislunar mission design is relatively new, little is known about the departure characteristics for
families of unstable periodic orbits modeled in the Earth-Moon Circular Restricted 3-Body Problem
(CR3BP). Additionally, previous work has determined that invariant manifolds from one Sun-planet
CR3BP system do not connect to manifolds in other systems in a practical amount of
time\cite{Koon:2000}. Consequently, new transfer design methodologies must be developed to connect
manifolds from planetary systems. Finally, since the current standard methods for interplanetary
transfers produce only point solutions, it would be beneficial to have new flexible methodologies
that provide families of transfers. Developing these new methodologies that connect invariant
manifolds across Sun-planet systems is key to achieving lower-energy deep-space transfers.

Consequently, this investigation aims to develop a design methodology for end-to-end transfers to
deep-space targets that provides families of solutions to compare the departure characteristics of
unstable Earth-Moon CR3BP periodic orbit families. This goal is broken down into the following
objectives:
\begin{enumerate}
    \item   \textbf{Establish a low-energy transfer design methodology between the cislunar region
			and Mars that utilizes CR3BP invariant manifolds.} This new transfer methodology
			includes a solution for bridging the gap between the invariant manifolds of Sun-planet
			CR3BP systems. Employing the CR3BP and patched models, the resulting solutions also
			exist in families, providing flexible mission design.
    \item   \textbf{Compare transfers that stage in intermediate Sun-Earth halo orbits to "direct"
			transfers.} Immediately once a trajectory departs the Earth-Moon CR3BP, it is in a
			region of space that is modeled by the Sun-Earth CR3BP. Sun-Earth invariant manifolds
			may depart their system faster than Earth-Moon manifolds that are propagated in the
			Sun-Earth model. Consequently, transfers that arrive at an intermediate Sun-Earth
			staging orbit are compared to those that take a more direct trajectory to determine the
			classification that has more favorable departure characteristics.
    \item   \textbf{Analyze and compare the Earth-Moon departure characteristics of various
			unstable CR3BP periodic orbit families within the framework of this investigation.} The
			ultimate goal of this investigation is to compare families of unstable Earth-Moon
			orbits to determine the ones that provide low-energy transfers to Mars with lower
			times-of-flight. The results inform future interplanetary and deep-space mission
			designs and lend insight into cislunar departure dynamics.

\end{enumerate}
To demonstrate the transfer methodologies, all the end-to-end cislunar-to-Mars transfers in this
investigation depart from various Earth-Moon CR3BP orbits but arrive at the same Sun-Mars $L_{1}$
northern halo orbit. Although this investigation primarily investigates cislunar-to-Mars transfers,
the techniques and developed methodologies apply to many other applications involving CR3BP systems
and other deep-space targets.

\section{Previous Contributions}
Traditionally, missions to Mars and other deep-space targets employ direct, impulsive transfers
that depart from the Earth or low Earth orbit. Porkchop plots are often applied in tandem with
patched conics to quickly provide point initial guesses for various epochs\cite{Drake:2009}. Earth
flybys have also been proposed by Landau and Longuski to reduce propellant
requirements\cite{Landau:2006}, while Fritz and Turkoglu harness gravity-assist maneuvers around
other bodies\cite{Fritz:2016}. While they are practical strategies for fast transfers, these
traditional methods highlight the need for innovative techniques to reduce propellant costs and
increase mission flexibility.

The application of multi-body dynamics to space trajectory design has evolved significantly since
its origins, leading to its application in several notable missions. One of the biggest
breakthroughs in multi-body astrodynamics occurred with the development of the CR3BP by Euler in
1722\cite{BarrowGreen:1997}. However, it took centuries before this model was finally incorporated
into trajectory design in the late 20th century. Some notable missions that have utilized
multi-body dynamics include the International Sun-Earth Explorer-3 (ISEE-3)\cite{Farquhar:1984},
Genesis\cite{Lo:2001}, ARTEMIS\cite{Woodard:2009}, and CAPSTONE\cite{Cheetham:2021}. Currently,
this model and associated techniques are also being employed to design the baseline trajectory and
operations for NASA's Gateway hub\cite{Zamora:2024,Boudad:2022,ZimovanSpreen:2022}. Dynamical
systems theory continues to play an increasing role in spacecraft mission design, offering new
possibilities for future exploration.

Within the context of interplanetary transfers and missions to deep-space targets, although
missions applying multi-body dynamical systems theory have yet to be flown, several authors have
developed/proposed multi-body dynamics methodologies. Miele and Wang exploit the dynamics of a
circular-restricted 4-body problem to numerically optimize transfers between Keplerian LEO and low
Mars orbits\cite{Miele:1999}. Going a step further, Conte starts from a lunar distant retrograde
orbit (DRO), a stable CR3BP orbit, but still employs porkchop plots to design direct transfers to
low Mars orbits\cite{Conte:2017}, while Esper and Aldrin harness aero-braking to arrive into a
Phobos DRO\cite{Esper:2019}. Interplanetary transfer design strategies utilizing multi-body
invariant manifolds started to appear around 2005 with Topputo et al., who investigated transfers
between CR3BP Sun-Earth and Sun-Mars Lyapunov orbits\cite{Topputo:2005}. Nakamiya et al. conducted
a similar investigation between Sun-Earth and Sun-Mars halo orbits in the Hills restricted 3-body
problem (HR3BP)\cite{Nakamiya:2010}. Haibin et al. added gravity assists and pseudo-manifolds to
aid in the transfer process between Sun-Earth and Sun-Mars halo orbits in the
CR3BP\cite{Haibin:2014}, while Kakoi et al. investigated transfers from Earth-Moon CR3BP halo
orbits to Mars\cite{Kakoi:2014}. To depart from a stable CR3BP orbit, Cavallari et al. utilize
Earth-Moon Lyapunov manifolds to facilitate transfers between lunar DROs and Sun-Mars Lyapunov
orbits\cite{Cavallari:2019}. Most recently in 2022, Scantamburlo et al. investigated Lyapunov
manifolds in the Elliptic Restricted 3-Body Problem (ER3BP) to connect the Sun-Earth and Sun-Mars
systems\cite{Scantamburlo:2022}, and Canales et al. employed a semi-analytical moon-to-moon
transfer design methodology to construct trajectories between CR3BP Sun-Earth and Sun-Mars halo
orbits\cite{Canales:2021a,Canales:2022}. Taking a slightly different approach, Lu et
al.\cite{Lu:2015}, Shimane and Ho\cite{Shimane:2022}, and Singh and Negi\cite{Singh:2024}
investigated the application of low-thrust maneuvers (instead of impulsive) to connect the
invariant manifolds of Sun-planet systems. Almost all of these previous studies treat the Sun-Earth
and Sun-Mars systems as coplanar, and none of them include analyses of other periodic orbit
families besides Lyapunovs and halos.

Several authors have also investigated connecting Earth-Moon to Sun-Earth orbits in their
respective CR3BP systems. Masdemont et al. go directly to CR3BP Sun-Earth libration point orbits
from Keplerian lunar orbits\cite{Masdemont:2021}. The previous study by Kakoi et al. utilizes a
patched CR3BP model to ballistically connect Earth-Moon and Sun-Earth halo orbits in their actual
respective planes\cite{Kakoi:2014}. Guo and Lei conducted a similar investigation to CR3BP
Sun-Earth libration point orbits\cite{Guo:2019}, whereas Pasquale et al. investigated heliocentric
escape options\cite{Pasquale:2021}. Finally, other authors have also investigated connections in
other dynamical models, such as Boudad et al. with the Bi-Circular Restricted 4-Body Problem
(BCR4BP)\cite{Boudad:2021}. These studies demonstrate the growing interest in leveraging multi-body
dynamical systems theory to connect various space regimes, offering valuable insights for future
mission designs.

\section{Overview of Current Work}
The main goal of this investigation is to compare families of unstable periodic orbits in the
Earth-Moon CR3BP to determine the ones that have desirable system departure characteristics. A
transfer design methodology is developed between the Earth-Moon and Sun-Mars CR3BP systems that
utilizes invariant manifolds to facilitate the orbit family comparison. This methodology consists
of two transfer types: one that stages at an intermediate Sun-Earth halo orbit and one that is
direct. Both types produce families of transfers instead of just point solutions, allowing for more
flexible mission designs. The resulting methodology and results apply to other deep-space targets
besides Mars, such as Venus or asteroids, and provide insight into general low-energy
interplanetary transfers.

The following chapters elaborate on the cislunar-to-Mars transfer design methodology and the CR3BP
Earth-Moon unstable orbit family analysis:
\begin{itemize}
	\item	\textbf{Chapter 2: Dynamical Models}\\
			This chapter introduces the dynamical models and coordinate frames that are employed in
			this investigation. The 2-Body Problem (2BP) and CR3BP are the main dynamical models
			utilized, with patched and blended model combinations that describe transitions between
			the systems. Within the CR3BP, the barycentric synodic rotating frame is primarily
			employed to represent trajectories, but a Sun-centered Ecliptic J2000 frame best
			represents the interplanetary transfers in their entirety.
	\item	\textbf{Chapter 3: CR3BP Dynamical Structures}\\
			The techniques from dynamical systems theory that are applied in this investigation are
			described here. These numerical techniques and dynamical structures are utilized in
			both the transfer design process and the subsequent analysis of the system departure
			characteristics. This chapter also includes examples of the unstable CR3BP periodic
			orbit families that appear throughout this investigation, as well as procedures for
			generating invariant manifolds from them.
	\item	\textbf{Chapter 4: Cislunar-to-Mars Trajectory Construction}\\
			Two existing transfer methodologies are adapted and combined to form the end-to-end
			cislunar-to-Mars transfer strategy. All of the transfers utilize a version of the
			moon-to-moon analytical transfer (MMAT) method developed by
			Canales\cite{Canales:2021b}. If transfers stage at an intermediate Sun-Earth orbit,
			near-ballistic transfers between the Earth-Moon orbits and the Sun-Earth halo orbits
			are constructed similarly to Kakoi's methodology\cite{Kakoi:2015}. This chapter also
			explains Hohmann transfers and their utility in designing direct transfers between the
			Earth and Mars.
	\item	\textbf{Chapter 5: Cislunar Departure Orbit Comparison}\\
			With a fully developed end-to-end transfer strategy, cislunar-to-Mars trajectories are
			constructed, originating from a variety of unstable Earth-Moon orbits. Several periodic
			orbit families, and orbits at different Jacobi constants (energy levels) within these
			families, are analyzed to determine those that provide favorable system departure
			characteristics compared to the others. This chapter also includes a comparison between
			the direct transfers and those that utilize intermediate staging orbits. It concludes
			with a comparison of the transfer results to those from the existing literature,
			including Hohmann transfers.
	\item	\textbf{Chapter 6: Conclusion}\\
			The main results and conclusions of the investigation are summarized along with
			recommendations for potential future work.
\end{itemize}
