% Acknowledgements page is optional but most theses include
% a brief statement of appreciation or recognition of special
% assistance.
\ifthenelse{\boolean{quick-or-debug}}{}
{
\begin{acknowledgments}
    First and foremost, I would like to thank my advisor Professor Kathleen Howell for inviting me
    into the research group and continuing to support me and provide me with wonderful
    opportunities. Her research insights and industry connections have proven invaluable during my
    time as a Master's student and I have enjoyed learning from her as I strive to contribute to
    the field of astrodynamics as she has.

    I am also grateful to my Master's committee members, Professor Carolin Frueh and Professor
    Kenshiro Oguri, for taking the time out of their busy schedules to provide insightful advice
    and feedback on my thesis research. My gratitude also extends to the Purdue University Gambaro
    Graduate Program of Aeronautics and Astronautics for providing me with office space, access to
    their technologies and facilities, and the Ross Fellowship which funded this graduate degree,
    and to Saber Astronautics for funding my research assistantship these last couple of years. 

    In addition to the faculty at Purdue, many others have contributed to my education and
    research. In particular, the members of the Multi Body Dynamics Research Group have listened
    to and provided feedback on hours of brainstorming and presentations over the past
    three-and-a-half years. Special thanks goes to Colton, Antony, JP, and Ricardo for coursework
    and research guidance, Liam, Josiah, and Lorin for support as we all defended together, and
    Nadia for encouraging me throughout the whole process.

    I would like to thank my good friend Isaac and Professor Clifford Whitfield for their support
    during my undergraduate studies at The Ohio State University and for encouraging me to attend
    graduate school in the first place. I would also like to acknowledge all of my friends and
    peers from Graduate InterVarsity Christian Fellowship, especially Weston, Edwin, and Emily,
    who formed my core life support group here in West Lafayette. For her contributions to my
    research and presentations, I want to extend special gratitude to Alicia, as well as for her
    continued encouragement and support in academics and in life, even from a distance.

    My family deserves the biggest recognition for getting me to where I am today. I would like to
    thank my parents for pushing me to be the man I am today, providing me with a loving home and
    stellar education, and always telling me how proud they are of me. I would like to thank my
    siblings as well for continuing to be my support system and never failing to bring joy and
    humor into my life. In addition to these, Grace has been the most constant source of support
    and motivation in my life through college and graduate school. I could not have made it this
    far without her, and I am forever grateful to have her in my life. Finally, all the glory and
    credit for my work goes to my creator and savior, my Lord Jesus Christ, who has brought me thus
    far and has great plans for my future.
\end{acknowledgments}
}