\begin{abstract}
With increasing interest in cislunar operations and exploration of deep space destinations like
Mars, a foundational understanding of cislunar dynamics and their potential for facilitating
departure from the vicinity of Earth is essential. This investigation addresses this need by
analyzing system departure characteristics from a variety of periodic orbit families with unstable
members in the Earth-Moon Circular-Restricted 3-Body Problem (CR3BP). Specifically, a
cislunar-to-Mars transfer methodology is developed, leveraging multi-body dynamical systems theory,
especially invariant manifolds of periodic orbits, to design lower-energy deep space transfers in
comparison to traditional methods. The proposed approach generates families of end-to-end
transfers that vary in total maneuver $\Delta v$ cost and time-of-flight, originating from
different unstable cislunar orbits. The tradespaces of these transfer families are then analyzed
and compared across various departure orbits to identify departure characteristics across orbit
families and energy levels (Jacobi constants). The analysis reveals certain unstable Earth-Moon
CR3BP orbit families with more favorable departure characteristics. Additionally, this
investigation compares the computed deep space transfer costs with those of traditional
interplanetary transfers and others from existing literature. Although this transfer design
strategy is specifically applied to Mars transfers in this investigation, the methodology is
broadly applicable to other deep space destinations. Furthermoe, the general findings on cislunar
departure characteristics have implications for mission designs to destinations beyond the
Earth-Moon region.
\end{abstract}
  